---
title: "deep learning for euro dollar prediction"
author: "kuldeep singh bhati"
output: html_document
---
The aim of the project is to train deep neural network using DN SAE model and predict next bar up and down for euro/dollar. 
Input data for the project use
https://github.com/kuldeepldec/deep-machine-learning-on-euro-dollar1



## Libraries required for the project
```{r}
library(caret)
library(deepnet)
library(quantmod)
library(rminer)
library(TTR)
```

###first read table euro/dollar 78 minute data data.
```{r}
price<-read.table("euro1.txt",header=TRUE,sep=",")
price1<-price
price=subset(price[,3:6])


```
###Calculating median and range for the bar
```{r}
Med <- (price[,2] + price[,3])/2
CO <- price[, 4] - price[, 1]
HL<-(price[,2] - price[,3])
```
###Add Med and CO prices to the matrix
```{r}
price <- cbind(price, Med, CO)
```
##Now producing indicators for input data,making an Input function

```{r}
Input<-function(p = 16){
  adx<-ADX(price, n = p)
  ar<-aroon(price[ ,c('High', 'Low')], n=p)[ ,'oscillator']
  cci<-CCI(price[ ,2:4], n = p)
  chv<-chaikinVolatility(price[ ,2:4], n = p)
  cmo<-CMO(price[ ,'Med'], n = p)
  macd<-MACD(price[ ,'Med'], 12, 26, 9)[ ,'macd']
  osma<-macd - MACD(price[ ,'Med'],12, 26, 9)[ ,'signal']
  rsi<-RSI(price[ ,'Med'], n = p)
  stoh<-stoch(price[ ,2:4],14, 3, 3)
  vol<-volatility(price[ ,1:4],n = p,calc="yang.zhang", N=96)
  xavg<-EMA(price[,4],n=p)
  trend<-price[,4]-xavg;
  atr5<-ATR(HLC(price),5)
  atr5<-atr5[,2]
  
  Input<-cbind(adx, ar, cci, chv, cmo, macd, osma, rsi, stoh,vol,xavg,trend,atr5)
#  Input<-cbind(adx, ar, cci, chv, cmo, macd, osma, rsi, stoh,vol)
  return(Input)
}
```



###to access In Function
```{r}
X<-Input()
```


##Making an out function for buy and sell signal, out signal take median price and calculate difference between two median prices.if value is postive assign 0 and if value is negative assign 0

```{r}
Out<-function(ch=0.0037){
  
  zz<-ZigZag(price[ ,'Med'], change = ch, percent = F, retrace = F, lastExtreme = T)
  n<-1:length(zz)
  
  # On the last bars substitute the undefined values for the last known ones
  for(i in n) { if(is.na(zz[i])) zz[i] = zz[i-1]}
  #Define the speed of ZigZag changes and move one bar forward
  dz<-c(diff(zz), NA)
  #If the speed >0 - signal = 0(Buy), if <0, signal = 1 (Sell) otherwise NA
  sig<-ifelse(dz>0, 0, ifelse(dz<0, 1, NA))
  return(sig)
}
```

```{r}
Y<-Out()
table(Y)
```
##clearing Na values using clearing function
```{r}
Clearing<-function(x, y){
  dt<-cbind(x,y);
  n<-ncol(dt)
  dt<-na.omit(dt)
  return(dt);  
}
```

```{r}
dt<-Clearing(X,Y)
```
##Balancing function check if 1 and 0 signal are equal or not, if they are not equal it insert 0 to columns of y with 1.
```{r}
Balancing<-function(DT){
  #Calculate a table with a number of classes
  cl<-table(DT[ ,ncol(DT)]);
  #If the divergence is less than 15%, return the initial matrix
  if(max(cl)/min(cl)<= 1.15) return(DT)
  #Otherwise level by the greater side
  DT<-if(max(cl)/min(cl)> 1.15){ 
         upSample(x = DT[ ,-ncol(DT)],y = as.factor(DT[ , ncol(DT)]), yname = "Y")
        }
  #Convert ? (factor) into a number
  DT$Y<-as.numeric(DT$Y)
  #Recode ? from 1,2 into 0,1
  DT$Y<-ifelse(DT$Y == 1, 0, 1)
  #Convert dataframe to matrix
  DT<-as.matrix(DT)
  return(DT);
}
```
###Seperating value of x and Y
```{r}
dt.b<-Balancing(dt)
```

```{r}
set.seed<-1245
X<-dt.b[ ,-ncol(dt.b)]
Y<-dt.b[ ,ncol(dt.b)]
t<-holdout(Y, ratio = 8/10, mode = "order")
prepr<-preProcess(X[t$tr, ], method = "spatialSign")
x.tr<-predict(prepr, X[t$tr, ])
y.tr<- Y[t$tr]; 
SAE<-sae.dnn.train(x = x.tr , y = y.tr , hidden = c(50, 50, 50), 
                     activationfun = "tanh",
                     learningrate = 0.7, momentum = 0.5, 
                     output = "sigm", sae_output = "linear", 
                     numepochs = 10, batchsize = 50)
X<-dt[ ,-ncol(dt)]
Y<-dt[ ,ncol(dt)]
x.ts<-predict(prepr, tail(X, 501))
y.ts<-tail(Y, 501)
pr.sae<-nn.predict(SAE, x.ts)

  #Variant +/- mean
sig<-ifelse(pr.sae>mean(pr.sae), -1, 1)
  #Variant 60/40#
#sig<-ifelse(pr.sae>0.6, -1, ifelse(pr.sae<0.4, 1, 0))
#sig.zz<-ifelse(y.ts == 0, 1,-1 )

comm<-tail(HL, 501)*100000*.01

bal1<-(tail(price[ ,'CO'], 501) * sig*100000)-comm



bal<-cumsum(bal1)+100000

plot(bal,  t = "l")





write.csv(tail(price1[ ,1], 501),'bal1.csv')

de<-cbind(tail(price[  ,1], 501),tail(price[  ,4], 501),sig,bal1,bal)

write.csv(de,'bal.csv')


#bal.zz<-cumsum(tail(price[  ,'CO'], 1) * sig.zz)
```




